Caribou Demographic Projection - interesting & informative title TBD

### 2022-12-15 analysis/paper/paper.Rmd
tweaking priors

```{r PriorKSDists, fig.cap="Prior parameter values should be set so that, given minimal monitoring data ('All' scenario: 1 year of 1 collar per year), the posterior survival distribution is similar to the distribution of simulated outcomes from the national model, measured here by Komogorov-Smirnov distance [ks.test function in @R_R_2022]. Low values of the mean and standard deviations of the prior distribution of the random effect of year on survival (sse=0.034784, ssv=0.01, $\\sigma^2_S$ in Table @ref(tab:priors)) meet this condition (Fig @ref(fig:priorAllFits). Priors should also be vague enough so that, given intensive monitoring of populations where survival is higher or lower than the national average ('High' and 'Low' scenarios: 15 years of 45 collars per year from 97.5% and 2.5% quantiles of the national model), posteriors reflect local survival, rather than priors from the national model. When the multiplier on the prior standard deviation of the survival intercept (lse: $\\beta^S_0$ in Table @ref(tab:priors)) is < 5, the prior is not sufficiently vague to meet the latter condition. Anthropogenic disturbance is set to 0 in these scenarios." , cache=TRUE}
knitr::include_graphics(here::here("figs/PriorKSDists.png"))

@@

```{r PriorHighFits, fig.cap="Posterior predictive survival distributions from the Bayesian model ('local') assuming intensive monitoring (15 years of 45 collars per year) of populations from the 97.5% quantile of the national model. In these examples, the multiplier on the prior standard deviation of the survival intercept (lse:$\\beta^S_0$ in Table @ref(tab:priors)) is 5 and  anthropogenic disturbance is 0. Bands show 95% posterior predictive intervals, black dots show true survival rates from the simulated population, and open triangles show observed survival rates.", cache=TRUE}
knitr::include_graphics(here::here("figs/SurvsQStarts45highlse5.png"))
```

@@

```{r PriorKSDistsRec, fig.cap="Prior parameter values should be set so that, given no monitoring data ('All' scenario), the posterior recruitment distribution is similar to the distribution of simulated outcomes from the national model, measured here by Komogorov-Smirnov distance [ks.test function in @R_R_2022]. XX values of the mean and standard deviations of the prior distribution of the random effect of year on recruitment (sre=XX, srv=XX, $\\sigma^2_R$ in Table @ref(tab:priors)) meet this condition (Fig @ref(fig:priorAllFits). Priors should also be vague enough so that, given intensive monitoring of populations where recruitment is higher or lower than the national average ('High' and 'Low' scenarios: 15 years of 135 cows per year from 97.5% and 2.5% quantiles of the national model), posteriors reflect local recruitment, rather than priors from the national model. When the multiplier on the prior standard deviation of the recruitment intercept (lre: $\\beta^R_0$ in Table @ref(tab:priors)) is XX, the prior is not sufficiently vague to meet the latter condition. Anthropogenic disturbance is set to 0 in these scenarios." , cache=TRUE}
knitr::include_graphics(here::here("figs/PriorKSDistsRec.png"))
```

```{r PriorAllFitsRec, fig.cap="Differences between posterior predictive recruitment distributions from the Bayesian model ('local') and simulated outcomes from the national model ('national'), assuming no monitoring. In these examples, the standard deviation the random effect prior (srv: $\\sigma^2_R$ in Table @ref(tab:priors)) is XX, and  anthropogenic disturbance is 0. Bands show 95% posterior predictive intervals ('local'), and the 2.5th and 97.5th percentiles for 500 sample populations from the national model.",  cache=TRUE}
knitr::include_graphics(here::here("figs/RecrQStarts1srv0.22.png"))
```

```{r PriorHighFitsRec, fig.cap="Posterior predictive recruitment distributions from the Bayesian model ('local') assuming intensive monitoring (135 cows per year for 15 years) of populations from the 97.5% quantile of the national model. In these examples, the multiplier on the prior standard deviation of the recruitment intercept (lre:$\\beta^R_0$ in Table @ref(tab:priors)) is XX and anthropogenic disturbance is 0. Bands show 95% posterior predictive intervals, black dots show true recruitment rates from the simulated population, and open triangles show observed recruitment rates.", cache=TRUE}
knitr::include_graphics(here::here("figs/RecrQStarts45highsrv0.22.png"))
```

>>>>

```{r PriorKSDists, fig.cap="Prior parameter values should be set so that, given minimal monitoring data ('All' scenario: 1 year of 1 collar per year), the posterior survival distribution is similar to the distribution of simulated outcomes from the national model, measured here by Komogorov-Smirnov distance [ks.test function in @R_R_2022]. Priors should also be vague enough so that, given intensive monitoring of populations where survival is higher or lower than the national average ('High' and 'Low' scenarios: 15 years of 45 collars per year from 97.5% and 2.5% quantiles of the national model), posteriors reflect local survival, rather than priors from the national model. When the multiplier on the prior standard deviation of the survival intercept (lse: $\\beta^S_0$ in Table @ref(tab:priors)) is 5, the prior is informative enough to meet the former condition, and vague enough to meet the latter. Given lse=5, low values of the mean standard deviations of the prior distribution of the random effect of year on survival (sse=0.034784, ssv=0.01, $\\sigma^2_S$ in Table @ref(tab:priors)) yield priors that meet both conditions (Figs @ref(fig:priorAllFits) and @ref(fig:priorLowFits)). Anthropogenic disturbance is set to 0 in these scenarios." , cache=TRUE}
knitr::include_graphics(here::here("figs/PriorKSDists.png"))

@@

```{r PriorLowFits, fig.cap="Posterior predictive survival distributions from the Bayesian model ('local') assuming intensive monitoring (15 years of 45 collars per year) of populations from the 2.5% quantile of the national model. In these examples, the standard deviation the random effect prior (ssv: $\\sigma^2_S$ in Table @ref(tab:priors)) is 0.01, and  anthropogenic disturbance is 0. Bands show 95% posterior predictive intervals, black dots show true survival rates from the simulated population, and open triangles show observed survival rates.", cache=TRUE}
knitr::include_graphics(here::here("figs/SurvsQStarts45lowssv0.01.png"))
```

@@

```{r PriorKSDistsRec, fig.cap="Prior parameter values should be set so that, given no monitoring data ('All' scenario), the posterior recruitment distribution is similar to the distribution of simulated outcomes from the national model, measured here by Komogorov-Smirnov distance [ks.test function in @R_R_2022]. Setting the multiplier on the prior standard deviation of the recruitment intercept (lre: $\\beta^R_0$ in Table @ref(tab:priors)) to 3, and values of the mean and standard deviations of the prior distribution of the random effect of year on recruitment to sre=0.23 and srv=0.22, respectively ($\\sigma^2_R$ in Table @ref(tab:priors)) allows us to meet this condition (Fig @ref(fig:priorAllFitsRec)). Priors should also be vague enough so that, given intensive monitoring of populations where recruitment is higher or lower than the national average ('High' and 'Low' scenarios: 15 years of 135 cows per year from 97.5% and 2.5% quantiles of the national model), posteriors reflect local recruitment, rather than priors from the national model. When the multiplier on the prior standard deviation of the recruitment intercept (lre: $\\beta^R_0$ in Table @ref(tab:priors)) is 1, the prior is not sufficiently vague to meet the latter condition (Fig @ref(fig:PriorLowFitsRec)). Anthropogenic disturbance is set to 0 in these scenarios." , cache=TRUE}
knitr::include_graphics(here::here("figs/PriorKSDistsRec.png"))
```

```{r PriorAllFitsRec, fig.cap="Differences between posterior predictive recruitment distributions from the Bayesian model ('local') and simulated outcomes from the national model ('national'), assuming no monitoring. In these examples, the standard deviation the random effect prior (srv: $\\sigma^2_R$ in Table @ref(tab:priors)) is 0.22, and  anthropogenic disturbance is 0. Bands show 95% posterior predictive intervals ('local'), and the 2.5th and 97.5th percentiles for 500 sample populations from the national model.",  cache=TRUE}
knitr::include_graphics(here::here("figs/RecrQStarts1srv0.22.png"))
```

```{r PriorLowFitsRec, fig.cap="Posterior predictive recruitment distributions from the Bayesian model ('local') assuming intensive monitoring (135 cows per year for 15 years) of populations from the 2.5% quantile of the national model.  In these examples, the standard deviation the random effect prior (srv: $\\sigma^2_R$ in Table @ref(tab:priors)) is 0.22, and  anthropogenic disturbance is 0. Bands show 95% posterior predictive intervals, black dots show true recruitment rates from the simulated population, and open triangles show observed recruitment rates.", cache=TRUE}
knitr::include_graphics(here::here("figs/RecrQStarts45lowsrv0.22.png"))
```
